### 2022-05-11 supplement.Rmd
Add jackknife analysis

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat[1:2, ])), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> jackknife_tab

>>>>

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> jackknife_tab
